\documentclass{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}

\newcommand{\rrtfunnel}{RRT-Funnel}

\usepackage{acronym}

% In text referencing
\usepackage{varioref}
\usepackage[draft]{hyperref}
\usepackage{cleveref}
\usepackage{color} % For colouring inkscape include (and more)
% \usepackage[style=ieee]{biblatex} % Needed for \textcite

% Math helpers
\usepackage{amssymb}    % Extra symbols
\usepackage{amsthm}     % Theorem-like environments
\usepackage{thmtools}   % Theorem-like environments, extends amsthm
\usepackage{mathtools}  % Fonts and environments for mathematical formulae
\usepackage{mathrsfs}   % Script font with \mathscr{}
\usepackage{dsfont}     % Double stroke font with \mathds{}
\usepackage{cancel}     % Cancel terms with \cancel, \bcancel or \xcancel
\usepackage{stmaryrd}   % Brackets


% IEEE package has no theorem definition
\newtheorem{definition}{Definition}[section]


% Optimization problem definition
\RequirePackage[nocomma]{optidef}

%% Operators
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\rank}{rank}



%% Delimiters
\DeclarePairedDelimiter{\p}{\lparen}{\rparen}          % Parenthesis
\DeclarePairedDelimiter{\set}{\lbrace}{\rbrace}        % Set
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}          % Absolute value
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}         % Norm
\DeclarePairedDelimiter{\ip}{\langle}{\rangle}         % Inner product, ideal
\DeclarePairedDelimiter{\sqb}{\lbrack}{\rbrack}        % Square brackets
\DeclarePairedDelimiter{\ssqb}{\llbracket}{\rrbracket} % Double brackets
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}         % Ceiling
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}      % Floor


%% Sets
\newcommand{\N}{\mathbb{N}}    % Natural numbers
\newcommand{\Z}{\mathbb{Z}}    % Integers
\newcommand{\Q}{\mathbb{Q}}    % Rational numbers
\newcommand{\R}{\mathbb{R}}    % Real numbers
\newcommand{\C}{\mathbb{C}}    % Complex numbers
\newcommand{\A}{\mathbb{A}}    % Affine space
\renewcommand{\P}{\mathbb{P}}  % Projective space

% The IEEE style uses \upshape for units
\newcommand{\IEEEunit}[1]{{\upshape #1}}

\newcommand{\mathEoS}{\, .} % End of sentence math delimeter

\def \Vectorized{} % Vectorize the math syntax.
%% Vectors
% \ifx \Vectorized \undefined
% \newcommand{\vect}[1]{#1}
% \renewcommand{\a}{a}
% \renewcommand{\b}{b}
% \renewcommand{\c}{c}
% \newcommand{\x}{x}
% \newcommand{\y}{y}
% \newcommand{\uin}{u}
% \newcommand{\w}{w}
% % \newcommand{\matr}[1]{\mathbf{#1}} % undergraduate algebra version
% \newcommand{\matr}[1]{#1}          % pure math version
% % \newcommand{\matr}[1]{\bm{#1}}     % ISO complying version
% \else % Vectorize defined.
\newcommand{\vect}[1]{{\mathbf{\mathsf{#1}}}}
\renewcommand{\a}{\mathbf{a}}
\renewcommand{\b}{\mathbf{b}}
\renewcommand{\c}{\mathbf{c}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\uin}{\mathbf{u}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\matr}[1]{#1} % undergraduate algebra version
% \newcommand{\matr}[1]{#1}          % pure math version
% \newcommand{\matr}[1]{\bm{#1}}     % ISO complying versionnewcommand{\w}{\mathbf{w}}
% \fi
\newcommand{\0}{\mathbf{0}}
\newcommand{\1}{\mathbf{1}}

% Optimization problem definitions
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\deter}{det}
\DeclareMathOperator{\lin}{lin}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\poi}{Poi}

\newcommand{\modelworld}{\ensuremath{\mathcal{W}}}
\newcommand{\modelrobot}{\ensuremath{\mathcal{A}}}
\newcommand{\modelobstacle}{\ensuremath{\mathcal{O}}}
\newcommand{\modelactionspace}{U}
\newcommand{\modelconfigurationspace}{\ensuremath{\mathcal{C}}}
% \newcommand{\modelconfigurationspacesub}[1]{\ensuremath{\mathcal{C}_{\textit{#1}}}}
\newcommand{\modelconfigurationspacefree}{\modelconfigurationspacesub{free}}
\newcommand{\modelconfigurationspaceobst}{\modelconfigurationspacesub{obst}}

\newcommand{\matlab}{\textsc{Matlab}\xspace}

\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{The Rapidly exploring Random Tree Funnel Algorithm for IEEE TRANSACTIONS and JOURNALS (March 2021)}

\author{\IEEEauthorblockN{Ole Petter Orhagen\IEEEauthorrefmark{1},
    Marius Thoresen\IEEEauthorrefmark{2}, and,
    Kim Mathiassen\IEEEauthorrefmark{2,3}
  }
  \IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Physics,
    University of Oslo, Oslo, Norway}
  \IEEEauthorblockA{\IEEEauthorrefmark{2}Norwegian Research Establishment, FFI,
    Postboks 25, 2027 Kjeller, Norway}
  \IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Technology Systems, University of Oslo, Kjeller, Norway}% <-this % stops an unwanted space
  \thanks{TODO -- Manuscript received December 1, 2012; revised August 26, 2015. 
    Corresponding author: M. Shell (email: http://www.michaelshell.org/contact.html).}}

% \thanks{This paragraph of the first footnote will contain the date on 
% which you submitted your brief for review. It will also contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.'' }
% \thanks{The next few paragraphs should contain 
% the authors' current affiliations, including current address and e-mail. For 
% example, F. A. Author is with the National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov). }
% \thanks{S. B. Author, Jr., was with Rice University, Houston, TX 77005 USA. He is 
% now with the Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu).}
% \thanks{T. C. Author is with 
% the Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA, on leave from the National Research Institute for Metals, 
% Tsukuba, Japan (e-mail: author@nrim.go.jp).}}

\maketitle

\begin{abstract}
  This paper shows the feasibility of combining robust motion primitives
  generated through the Sums Of Squares programming theory with a discrete
  Rapidly exploring Random Tree algorithm. The generated robust motion
  primitives, referred to as funnels, are then employed as local motion
  primitives, each with its locally valid Linear Quadratic Regulator (LQR)
  controller, which is verified through a Lyapunov function found through a Sum
  Of Squares (SOS) search in the function space. These funnels are then combined
  together at execution time by the Rapidly-exploring-Random-Tree (RRT) planner,
  and is shown to provide provably robust traversal of a simulated forest
  environment. The experiments benchmark the RRT-Funnel algorithm against an RRT
  algorithm which employs a maximum distance to the nearest obstacle heuristic
  in order to avoid collisions, as opposed to explicitly handling uncertainty.
  The results show that employing funnels as robust motion primitives outperform
  the heuristic planner in the experiments run on both algorithms, where the
  RRT-Funnel algorithm does not collide a single time, and creates shorter
  solution paths than the benchmark planner overall, although it takes a
  significantly longer time to find a solution. Index Terms— Collision
  avoidance, Motion planning, Nonlinear control systems, Robot control
\end{abstract}

\begin{IEEEkeywords}
  Collision avoidance, Motion planning, Nonlinear control systems, Robot control
\end{IEEEkeywords}

\input{sections/PreIntro.tex}

% \section{Method}
\label{sec:Method}
\input{sections/Method.tex}


\section{Experiments}
\label{sec:Experiments}
\input{sections/Experiments.tex}

\section{Results}
\input{sections/Results.tex}

\section{Discussion}
\input{sections/Discussion.tex}
The discussion goes here\ldots

\section{Conclusion}

This paper has shown that the \rrtfunnel{} motion planning algorithm does
provide robust feedback motion planning for a nonlinear dynamic system. It shows
that a motion planning algorithm employing discrete verified robust motion
primitives outperforms a traditional motion planning algorithm significantly in
terms of safe traversal through a known environment. It has also shown that the
robust planner is only reliable up to and including its uncertainty bounds, and
will start misbehaving, just like the benchmark motion planner, once the
uncertainty assumptions on the algorithm are broken. All in all, it is shown
that the \rrtfunnel{} algorithm is a viable option for a global motion planner
in an uncertain environment.

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibtex/zotero}

\begin{IEEEbiographynophoto}{Ole Petter Orhagen}
  Ole Petter Orhagen was born in Gjovik, Norway in 1989. He received a B.S. in
  Informatics, and M.S degree in cybernetics from the University of Oslo, in
  2017 and 2019.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Marius Thoresen}
  Marius Thoresen Marius Thoresen received a Master’s degree in engineering
  cybernetics from the Norwegian University of Science and Technology in 2015.
  In 2015, he started working as a researcher at the Norwegian Defence Research
  Establishment with UGVs and autonomous systems. In 2019 he started a PhD with
  the Norwegian University of Science and Technology, with motion planning for
  UGVs in rough terrain as his topic of research.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Kim Mathiassen}
  Kim Mathiassen Kim Mathiassen received a
  Masters degree in engineering cybernetics from
  the Norwegian University of Science and Technology in 2010 and a PhD in robotics from the
  University of Oslo in 2017. His PhD thesis was
  on a semi-autonomous system for diagnostics
  and treatment using medical ultrasound.
  In 2015 he started working at the Norwegian Defence Research Establishment with
  Unmanned Ground Vehicles (UGV) and autonomous systems. In addition to his research
  position he is an associate professor at the University of Oslo teaching
  advanced robotics. His current research interests span from low level
  robot control to high level planning and reasoning.
 \end{IEEEbiographynophoto}



\end{document}
