%!TEX root=../rrtfunnel-transmag.tex

\section{Introduction}
\IEEEPARstart{M}{otion} planning concerns the problem of finding a dynamically
feasible path from an initial configuration to a defined end state in a safe
manner. In order for a motion planner to handle real world motion planning tasks
it needs to handle the uncertainty that comes with a real-life planning problem.
This is especially difficult for nonlinear dynamical systems. Knowledge of
the system's state, the environment and the dynamics of the system are all uncertain to
some degree. Limited measurement precision and use of imperfect world and vehicle models will therefore leave error terms in the state and world estimations.
Thus, in order for a planner to guarantee safe traversal through a real world environment, a motion planner needs to handle uncertainties.

In the face of uncertainty, some planners choose to ignore these error sources
and instead apply heuristics such as maximizing the distance to the obstacles in
the environment or setting a fixed safety radius \cite{Hoy2015ClutteredEnvironmentSurvey}.
However, this adds the disadvantage that the plans can become overly conservative. 
Explicitly handling the uncertainties in the planning stage enables the planner to employ more aggressive maneuvers, such as going through two obstacles that are close together, as opposed to going around the difficult area. 
If uncertainties are accounted for, going straight through is an acceptable maneuver for a planner that has guarantees on the whereabouts of the dynamical system, and hence is not afraid to get close to an obstacle.

%\subsection{Literature Review}


%\subsubsection{Robust Motion Planning}

% This work is a part of the broader field of planning under uncertainty. The
% algorithms are further classified depending on classes of uncertainty they can
% handle. That is, uncertainty in the planning environment, uncertainty in the
% model, uncertainty in sensing, and uncertainty in the map.
%
% kma - Det ser ikke ut som du gpr igjennom tidligere arbeid som du beskriver over, men klassifiserer dem teer RRT og SOS


%\subsubsection{RRT with Robust Motion Primitives}
In motion planning, there is a separation between global and local methods \cite{Hoy2015ClutteredEnvironmentSurvey}, where global methods assumes a known map of the environment and local methods assumes only local knowledge. 
Thus, global methods can plan paths from the start state to the goal, whereas local methods can only plan a part of the way. 
As local methods does explicitly consider the end goal in the planning, they can be more susceptible to getting trapped in local minima.

Previous efforts to handle uncertainties in global path planning include using the Rapidly-exploring Random Tree (RRT) algorithm with robust motion primitives. 
Tedrake~\cite{tedrakeLQRtreesFeedbackMotion2009} creates a tree consisting of robust LQR (linear-quadratic regulator) controllers, in order to guarantee safe traversal of the primitives in the tree given a dynamic system. 
Van den Berg~\cite{vandenbergLQGMPOptimizedPath2011} has a similar approach of creating motion primitives where LQR is used, and a Gaussian process is used to model  uncertainty, allowing reasoning about the primitives.
Luders generate robust motion primitives in real-time for an \textit{RRT*} algorithm through chance constraints in~\cite{luders2013robust}, but also ensures asymptotic optimality.
Another robust extension to the \textit{RRT} algorithm can be found in Melchior~\cite{melchior2007particle}, where each extension to the tree is treated as a stochastic process, and simulated multiple times, and since pruned based on the expected probability of successful execution.


%\subsubsection{SOS and Robust Motion Planning}

A recent approach to the local path planning problem has been to use Sum of Squares (SOS) theory with motion planning.
In Tedrake~\cite{tedrakeLQRtreesFeedbackMotion2009} a tree of LQR-controllers is created, in order to safely take a dynamical system from one intial state to a final state. 
In~\cite{majumdarFunnelLibrariesRealtime2017}, Majumdar expands upon this idea and seeks to limit the size of the area in which a controller will take a dynamic system, while at the same time giving guarantees of success.
This enables real-time motion planning in highly complex environments with advanced vehicle models. 
The current research on the topic is limited, but interesting due to the formal general robustness guarantees it can provide.

However, the method is a local method, and thus has a limited planning horizon.
In~\cite{majumdarFunnelLibrariesRealtime2017}, a simulated experiment with large-scale environments is conducted, but only by repeating the local process several times. 
If we instead can use the theory and framework introduced here and combine it with a global planner, we can achieve longer planning horizons and thereby reduce likelihood of getting trapped in local minima .

This paper builds upon the work done on verifying regions of attraction---referred to as \emph{funnels}---for nonlinear dynamical systems through the use of Lyapunov functions. Verification is achieved for a polynomial system through the use of SOS programming.
We combine the theory of funnels with a discrete RRT motion planner in order to provide a provably robust global motion planner for a nonlinear dynamical system. 
To the best of the authors' knowledge, this is the only known RRT algorithm which implements verified reachable sets as discrete motion primitives as extension operators for the a RRT algorithm. 
The novel method is then compared with a RRT algorithm that maximize the distance to the nearest obstacles in order to handle uncertainty.
The result of this work is the RRT-Funnel motion planning algorithm, a discrete motion planning algorithm which can guarantee safe passage through an obstacle space, given the assumption that the uncertainty in the system is bounded. 
The funnel definitions in this paper is taken from a series of articles on funnels~\cite{Tobenkin_2011,tedrakeLQRtreesFeedbackMotion2009,
  majumdarRobustOnlineMotion2013,
  majumdarFunnelLibrariesRealtime2017,ahmadi2014dsos}, with the main focus being
on \cite{majumdarFunnelLibrariesRealtime2017}.



